### 2016-11-04 paper/intro.tex
quick pass on intro

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.
For large IT organizations, the alternative of renting server farms,
or even building one, is a potential escape to the regression testing
problem.  However, for open-source projects and for projects of
smaller organizations with lower budgets for building testing
infrastructures, this alternative may not be as attractive.

\newcommand{\numSubjs}{143}

Motivated by this potential gap in regression testing practice, we
first studied (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
criteria.)  Our experimental results indicate that long-running test
suites (taking longer than 5m\Fix{check if Ekstazi paper also used
  this value and cite} to complete) are not rare~--~\Fix{17\%} of the
projects we analyzed contain long-running test suites.  From this
result we investigated (2) how frequently long-running test suites use
parallelization\Mar{justify why parallelization}.  Our results
indicate that \Fix{80\%} of the long-running test suites do use
parallelization to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in each of these projects.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the effects of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related with parallelization that could justify
adoption resistance.

>>>>

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.
For large IT organizations, the alternative of renting server farms,
or even building one, is a potential escape to the regression testing
problem.  However, for open-source projects and for projects of
smaller organizations with lower budgets for building testing
infrastructures, this alternative is not as attractive.

%% eventually move this to macros.tex
\newcommand{\numSubjs}{143}
\newcommand{\numLongRunning}{\Fix{17\%}}
\newcommand{\percentParallelForLongRunning}{\Fix{80\%}}

Motivated by this potential gap in regression testing practice, we
first studied (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
methodology.)  Our experimental results indicate that long-running
test suites (taking longer than 5m to complete\Fix{check if Ekstazi
  paper also used this value and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  From this result we investigated (2) how
frequently the projects we considered use parallelization to speedup
test runs.  We parsed build files of projects to identify usage of
parallelism. \Mar{justify parallelization}.  Our results indicate that
\percentParallelForLongRunning{} of long-running test suites do use
parallelism to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the effects of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related with parallelization that could justify
adoption resistance.
